Template report example

### 2023-09-03 dev/dev_template_report.Rmd
Template project rmarkdown report

---
title: "ntsIUTA Report Template"
author:
  name: "Ricardo Cunha"
  affiliation: "Insitut für Energie- und Umwelttechnik e.V. (IUTA)"
  email: cunha@iuta.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

@@

path_extdata <- system.file(package = "streamFind", dir = "extdata")
logo <- file.path(path_extdata, "logo_iuta.png")

knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 9, results = "asis")

path_wd <- getwd()
```

```{r logo, echo=FALSE}
htmltools::img(
  src = knitr::image_uri(logo),
  alt = "logo",
  style =
    paste0("
      margin-left:inherit;
      position:absolute;
      top:60px;
      left:740px;
      width:", 100, "px;
      height:", 100*(216/207), "px;"
    )
)
```

@@

```{r libraries, include=FALSE}

library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(plotly)
library(streamFind)

@@

```{r exCode}

@@

The `knitr::kable` function can be used for displaying tables, see table \@ref(tab:exTable). Consult <https://haozhu233.github.io/kableExtra/awesome_table_in_html.html> for other costumization options.
Table caption is added with the argument `caption` of the `kable` function.

```{r exTable}

@@

knitr::kable(df, caption = "Example of table caption.") %>%
kable_styling(
  font_size = 12,
  bootstrap_options = c("striped", "hover", "condensed", "responsive"),
  fixed_thead = TRUE
) %>%
  scroll_box(width = "100%", height = "600px")

@@

```{r exGgplot, fig.cap="Plot caption example"}

@@

```{r exPlotly, fig.cap="Plot caption example"}

@@

***
**Insitut für Energie- und Umwelttechnik e.V.**  
A: Bliersheimer Str. 58 - 60, 47229 Duisburg  
T: (02065) 418 - 0

>>>>

---
title: Template report example
subtitle: subtitle
author:
  name: author
  email: email@example.com
  affiliation: "name <br> address"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    theme: paper
editor_options: 
  chunk_output_type: console
---

@@

# Libraries
library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(plotly)
library(streamFind)

# Variables
logo <- NA_character_

# Global options
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 9, results = "asis")

# Working directory
path_wd <- getwd()

# Add logo file
path_extdata <- system.file(package = "streamFindData", dir = "extdata")
logo <- file.path(path_extdata, "logo_iuta.png") #207 x 216 px
```

```{r logo, echo=FALSE}
if (!is.na(logo)) {
  htmltools::img(
  src = knitr::image_uri(logo),
  alt = "logo",
  style =
    paste0("
      margin-left:inherit;
      position:absolute;
      top:60px;
      left:740px;
      width:", 100, "px;
      height:", 100*(216/207), "px;"
    )
  ) 
}
```

@@

@@

```{r exampleCode}

@@

The `knitr::kable` function can be used for displaying tables, see table \@ref(tab:exampleTable). Consult <https://haozhu233.github.io/kableExtra/awesome_table_in_html.html> for other costumization options.
Table caption is added with the argument `caption` of the `kable` function.

```{r exampleTable}

@@

knitr::kable(df, caption = "Example of table caption.") %>%
kable_styling(
  font_size = 12,
  bootstrap_options = c("striped", "hover", "condensed", "responsive"),
  fixed_thead = TRUE
) %>%
  scroll_box(width = "100%", height = "350px")

@@

```{r examplePlot, fig.cap="Plot caption example"}

@@

```{r examplePlotly, fig.cap="Plot caption example"}

@@
